---
title: "linear model from Web"
author: "Davy D"
date: "spring 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```
# Introduction
We will produce three equation models to get

1. sim score based on arm strength  
2. sim score based on grip strength  
3. sim score based on both arm and grip strength.  

For each model we will predict sim for arm =88, grip =94.

## Model 1 SIM~ARMS
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
We have numerical response (sim score) and numerical explanatory variables (arm and grip strength)
So we use the numerical-numerical helper file.

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

There is a positive relationship between SIMS and ARMS if this where a perfect linear relationship all points would be a straight line, the correlation between SIM and ARM strength is 0.

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

This summarizes the correlation between degree of correlation between ARM strength and SIMS score being around .7

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
The p-value of this coefficient of arm 0.0000000000000002


#### Predict at target point

```{r}
SIMSpredict = predict.lm(model.1,newdata = data.frame (ARM = 88, GRIP = 94), interval = "confidence")
print (SIMSpredict)
```

The prediction for ARM = 88 and GRIP = 94 is .71

#### scatterplot with model fit

```{r}
plot(SIMS~ARM,data=data)
abline(model.1,col="green")
```  

This is a scatter plot with a function on it, at ARM strength 88 the 95 percent confidence interval is between 0.49 and 0.92.

## Model 2 SIM~GRIP

```{r}
model.2 <- lm(SIMS~GRIP + ARM ,data=data)
summary.lm(model.2)
``` 

### Now add in scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```


### Numerical results 


### Inferential  (Build model.2)

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```  

#### predict model.2 at target point

#### now add the model fit to our plot for model.2
  


## Model 3 SIM~ARM+GRIP



### Numerical results (cor)


`The table shows SIMS correlates with GRIP in a positive manner (0.64) and SIMS correlates with ARM also in a positive manner, (0.69) this says these variables are useful in predictings SIMS



PLOT SHOWS GRIP AND ARM ARE NOT INDEP SO THIS IS NOT NECESSARILY A GOOD MODEL  
### Inferential  (Build 2-dimentional model.3)

#### predict model.3 at target point
  


## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

